Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-14 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
fixing some words in the abstract

\begin{abstract}
Volunteer computing is extensively used in science and industry, but it
still has a long way to go in order to become a mainstream
technology in the same way the cloud technologies in general are. %I have changed "have" to "are"
The lack of general purpose and open source tools with built-in analytics 
could be one of the reasons of why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, entirely written in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface. An enhanced implementation, {\sf NodIO-W$^2$} is also
presented, this version leverages the HTML 5 Web Workers specification
to execute several clients per browser in the background, so that the the number of
generations per user could be improved. The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follows by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}

>>>>

\begin{abstract}
Volunteer computing is extensively used in science and industry, but it
still has a long way to go in order to become a mainstream
technology in the same way the cloud technologies in general are. %I have changed "have" to "are"
The lack of general purpose and open source tools with built-in analytics 
could be one of the reasons of why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, entirely written in JavaScript, which needs
minimal server support to work and that is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface. An enhanced implementation, {\sf NodIO-W$^2$} is also
presented; this version leverages the HTML5 Web Workers specification
to execute several clients per browser in the background, so that the the number of
generations per user could be improved. The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follows by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}
